Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-03-03 ms.tex
minor edits

\begin{itemize}
\item We include all publicly available NEOWISER W1 and W2 exposures, 
approximately doubling the number of input L1b frames relative to the 
\cite{lang14} processing.
\item We adopt custom zero points based on repeat photometry at the ecliptic 
poles. In contrast, the \cite{lang14} unWISE processing adopted zero points 
based on the L1b header metadata.
\item We explicitly reject exposures contaminated by the Moon and/or solar 
system planets. No such rejection was included in the \cite{lang14} unWISE 
W1/W2 coadds, although these and other artifacts were addressed to some extent 
via general-purpose outlier rejection.
\item In this work we attempt to recover Moon-affected frames by applying 
polynomial background level corrections to the contaminated exposures.
\end{itemize}

@@

It is important to quantify the effect of increased coverage on
the W1/W2 depths achieved by catalogs based on our AllWISE+NEOWISER coadds 
relative to those based on the AllWISE-only coadds of \cite{lang14}. A
complete characterization should systematically explore a range of 
ecliptic and galactic latitudes, to consider the full spectrum of interplay
between decreased statistical noise and confusion. For isolated sources in the 
sky noise limit, we would expect a doubling of the W1/W2 imaging data
to increase the depth in each band by 0.38 mag.

The only existing catalogs based on our AllWISE+NEOWISER coadds
are those from DR2 of the DECam Legacy Survey\footnote{http://legacysurvey.org} 
\citep[DECaLS,][]{decals}, which include W1-W4 forced photometry for all
optically detected sources. On the other hand, optical sources in DECaLS DR1
are accompanied by forced photometry of the \cite{lang14} unWISE coadds. 
Therefore, comparing the uncertainties on W1/W2 fluxes in DR2 versus DR1 can 
allow us to obtain estimates of the forced-photometry depth increases for 
regions of low ecliptic and high galactic latitude.

>>>>

\begin{itemize}
\item We include all publicly available NEOWISER W1 and W2 exposures, 
approximately doubling the number of input L1b frames relative to the 
\cite{lang14} processing.
\item We adopt custom zero points based on repeat photometry at the ecliptic 
poles. In contrast, the \cite{lang14} unWISE processing adopted zero points 
extracted from the L1b header metadata.
\item We explicitly reject exposures contaminated by the Moon and/or solar 
system planets. No such rejection was included in the \cite{lang14} unWISE 
W1/W2 coadds, although these and other artifacts were addressed to some extent 
via general-purpose outlier rejection.
\item In this work we attempt to recover Moon-affected frames by applying 
polynomial background level corrections to the contaminated exposures.
\end{itemize}

@@

It is important to quantify the effect of increased coverage on
the W1/W2 depths achieved by catalogs based on our AllWISE+NEOWISER coadds 
relative to those based on the AllWISE-only coadds of \cite{lang14}. A
complete characterization should systematically explore a range of 
ecliptic and Galactic latitudes, to consider the full spectrum of interplay
between decreased statistical noise and confusion. For isolated sources in the 
sky noise limit, we would expect a doubling of the W1/W2 imaging data
to increase the depth in each band by 0.38 mag.

The only existing catalogs based on our AllWISE+NEOWISER coadds
are those from DR2 of the DECam Legacy Survey\footnote{http://legacysurvey.org} 
\citep[DECaLS,][]{decals}, which include W1-W4 forced photometry for all
optically detected sources. On the other hand, optical sources in DECaLS DR1
are accompanied by forced photometry of the \cite{lang14} unWISE coadds. 
Therefore, comparing the uncertainties on W1/W2 fluxes in DR2 versus DR1 can 
allow us to obtain estimates of the forced-photometry depth increases for 
regions of low ecliptic and high Galactic latitude.
